% !TEX root = ./sub-main.tex
\documentclass[main.tex]{subfiles}

\begin{document}
    \section{Credit Risk Mitigation}
    
    Credit risk mitigation is actions taken by dealers 
    with the purpose of reducing their exposure to counterparty credit risk.
    Reducing counterparty credit risk has important implications.
    From a risk management point of view,
    the amount of counterparty exposure a dealer is willing, or allowed, to take on 
    is determined by the default risk of the counterparty 
    as well as the risk appetite of the dealer's institution.
    When this limit is set, the dealer will be able to obtain some amount of trades,
    before the risk limit is met.
    However, if the dealer cleverly applies credit risk mitigations,
    she might be able to obtain an even larger amount of trades,
    increasing her capacity to do business.
    Even if the dealer does not increase her holdings after applying credit risk mitigations,
    she will have reduced her counterparty credit risk,
    which could lead to her capital requirements being reduced.
    Having motivated the use of credit risk mitigations,
    this section will discuss three methods of mitigating credit risk;
    namely, netting sets, collateralization, and trading through a central counterparty.

    \subsection{Netting}
        A netting set is a group of trades whose value can be \textit{netted off}, 
        when a counterparty defaults.
        When netting off a collection of trades, the trades' values are aggregated,
        offsetting payables with receivables, such that,
        only one single amount is owed if a counterparty defaults.
        Netting sets are important to credit exposure, 
        as counterparty risk is settled at each set;
        therefore, netting is central to mitigate credit risk.
        To see this consider the following example.

        \begin{example}    
        A derivatives dealer has two different netting sets, 
        referred to as netting set X and netting set Y.
        The dealer sells a derivative with netting set X and, 
        not wanting the exposure, buys the same derivative with netting set Y.
        Therefore, the market risk is eliminated, so the dealer is neutral from this point of view.

        However, the credit risk exposure metric for the dealer's entire portfolio will include 
        the credit risk metric for both netting set X and Y considered separately.
        If instead the derivative is bought with netting set X,
        both the market risk and the credit risk will be offset.
        \end{example}

        Hence, the standalone credit risk of a trade might not give the full picture,
        as the trade will be part of a netting set with offsetting cash flows.
        Instead, the dealer can evaluate how much the credit risk measure
        would change if the trade was obtained; this is the incremental credit risk measure.
        By evaluating the incremental credit risk measures from the trade,
        potential netting benefits can be accounted for. 

        By strategically considering netting benefits the dealer can reduce her credit risk. 
        Additionally, the dealer can further reduce her exposure by, in advance,
        taking custody of some of her receivables from the counterparty.
        Then, the receivables are protected from other creditors if the counterparty defaults.

    \subsection{Collateralization and Securing Positions}
        Credit risk can be reduced significantly, and even eliminated completely,
        if the counterparty provides some form of security, which the dealer has priority to.
        Should the counterparty default, the dealer can use the security to cover any
        outstanding receivables from the counterparty. 
        Likewise, the dealer can provide security to a counterparty and 
        therefore receive better prices.
        The type of security used, and the circumstances 
        under which they are available to the other entity, can vary significantly.
        This section will describe two common ways of providing security, 
        namely \textit{repo transactions} and \textit{CSA agreements}.

        \subsubsection{Repurchase Agreements}
        A repo, short for repurchase agreement, is a trade in which a dealer 
        sells bonds to a counterparty,
        with the promise of buying them back at a fixed price on a fixed date.
        The counterparty will be referred to as the lender.
        The dealer receives cash from the lender and the lender receives the bonds,
        which it uses as security for the money lent to the dealer. 
        If the dealer defaults and fails to honour her obligation to buy back the bond,
        the lender can keep it and possibly liquidate it to recover the cash lent. 
        Repos can be used as a form of short-term secured borrowing for the seller
        and an opportunity for the lender to invest funds for a customized period of time. 
        Traders can use repos to apply leverage by buying long positions in bonds 
        which they then post as the collateral in the repo. 

        Purchasing bonds through repos is beneficial to the dealer,
        as she can fund her purchase at the secured borrowing rate,
        which is going to be lower than the unsecured borrowing rate.

        \subsubsection{CSA Agreements}
        Derivative transactions can be secured in a similar way 
        if the counterparties agree upon and adhere to a Credit Support Annex, CSA, agreement.
        A CSA defines terms and conditions for collateral postings between counterparties, 
        such that transaction between them are secured.
        Most CSA agreements require both entities in the transaction to post collateral 
        if they have negative exposure to their counterparty. 
        This is important for derivatives transactions that can have both 
        positive and negative mark-to-market values, 
        such that an entity can be both positively and negatively exposed to the counterparty
        during the lifetime of the derivative.
        When collateral is posted through a CSA, it provides a couple of benefits for the receiver.
        Most obvious, the receiver can use the collateral to cover losses incurred 
        due to the default of the other party.
        However, another important feature of CSA agreements is the ability of dealers to
        \textit{rehypothecate} collateral.
        To rehypothecate collateral refers to passing it on to other parties that
        require collateral from the dealer.
        By doing this, the dealer can reduce, or even eliminate, the need for providing her own funds
        for supporting other CSA agreements. 
        This mechanism will prove to be very important in the context of funding value adjustments.

        Whether collateral should be posted, and how much should be posted, 
        depends on a number of parameters defined in the CSA agreement
        as well as external values due to the general market conditions.
        The parameters deemed most important to this paper will be described in the following.
        \begin{description}
            \item[Threshold:] 
            the level of positive or negative exposure above which collateral will be posted. 
            Allowing a higher threshold will also yield a higher exposure;
            however, only to the extent of the threshold size. 
            Hence, the threshold is the amount of exposure the dealer can accept being uncollateralized.
            Typically, CSA agreements between banks will have zero thresholds, 
            such that derivative transactions are fully collateralized.
            
            \item[Minimum transfer amount:] 
            how much positive or negative exposure the counterparties can have before collateral is posted;
            hence, it is the smallest amount of collateral that can be exchanged between counterparties.
            It is often used to avoid the operational overhead from posting collateral for negligible amounts,
            but, like the exposure threshold, it comes at the cost of increased exposure.

            This parameter is also a threshold and the difference between this
            and the actual threshold-parameter might seem subtle.
            The threshold refers to the exposure directly due to the mark-to-market value,
            however the minimum transfer amount considers the exposure after taking into 
            account the mark-to-market, the current collateral posted, and the threshold.

            \item[Independent amount:]
            an amount of collateral posted regardless of the derivative's mark-to-market value. 
            Its purpose is to account for potential unexpected market moves
            that could lead to under-collateralization.
            A party posting an independent amount decreases the exposure for the other party
            since it works as an initial buffer for credit risk mitigation.
            This quantity can also be referred to as \textit{the initial margin}, 
            however, strictly speaking, 
            that term tends to be used when clearing through a central counterparty,
            which will be described in the following section.
            Conceptually, the two quantities are the same, and throughout this paper
            the two terms will be used interchangeably as the difference is subtle
            and irrelevant for the purposes of the analysis. 

            \item[Collateral call frequency:]
            how often a party can submit calls for collateral.
            Typically, CSA agreements between banks will have daily call frequency;
            other organizations will have a lower frequency simply due to the operational burden
            of posting collateral as often as daily. 
            A lower call frequency means larger exposure to the counterparty,
            as the mark-to-market will have longer to diverge from the collateral posted 
            at the last valuation date.
        \end{description}

        Besides the parameters mentioned, CSA agreements will have specifications about the type of collateral allowed,
        e.g. which currencies can be posted or if government bonds can be used as collateral,
        as well as a procedure to follow if one of the parties is downgraded to a specified credit rating.
        It should be emphasized that the parameters might not be identical for each party
        if one party has a different credit quality than the other.
        If the credit qualities differ a lot, the CSA agreement might even be one-directional,
        such that only one party posts collateral.

        For the purpose of benchmarking collateralization schemes, 
        it will be helpful to define the theoretical concept of a \textit{perfect} CSA agreement.
        A perfect CSA will have zero threshold and zero minimum transfer amount.
        In addition, it will have a, so to speak, infinitely high collateral call frequency,
        meaning that collateral calls are made continuously and instantly 
        whenever there is the slightest change in the mark-to-market value. 
        If the counterparty instantly meets collateral calls and have no cure period,
        a perfect CSA agreement would eliminate the exposure to the counterparty
        and therefore the credit risk.
        Of course, this is merely a theoretical construct, as all sorts of frictions introduce delays,
        which would break the assumptions.
        Nonetheless, the idea of a perfect CSA will be helpful to have as a reference,
        when introducing funding value adjustments.

        As a final remark on this topic,
        it is important to note that this paper will have a rather idealized perception of collateralization.
        It is assumed that each collateral payment perfectly offsets the mark-to-market value,
        which is not necessarily the case in the real world,
        where there might be disputes over the value of different instruments.
        In addition, it is assumed that calls for collateral will instantly be answered
        by either the required collateral or the counterparty's default. 
        In reality, collateral will not arrive instantly, and a period of time will pass between
        the point where the counterparty does not post collateral to the point where it actually defaults.
        All of these frictions of the real world increase the credit risk to the counterparty
        and must be considered in practical applications. 
        In the context of funding value adjustments, 
        they would simply be part of a large pool of contributors to funding frictions,
        and there is no value lost in assuming them non-existing;
        however, a great amount of simplicity is gained.

    \subsection{Clearing Through Central Counterparty}
        A \textit{Central Counterparty}, CCP, is an institution
        providing clearing for standardized OTC derivative contracts
        and therefore works as the intermediary in a transaction.
        A CCP is a counterparty to both the buyer and the seller in a transaction 
        and guarantees the terms of the trade by providing compensation to one party when the other party defaults.
        It does so by collecting collateral from the buyer and seller to cover potential losses.
        From a collateralization perspective, central clearing is very similar to trading through CSA agreements
        since collateral must also be posted to the CCP in order to support movements in the mark-to-market value.
        In the context of central clearing, this collateral is known as variation margin.
        Central clearing can also support the posting of an independent amount of collateral 
        known as initial margin.
        Unlike the independent amount of a CSA, initial margin is possibly dynamic 
        as it can depend on the riskiness of the parties, 
        such that increases in risk measures might trigger calls for additional initial margin.
        \\
        When using a CCP, rehypothecation of collateral is not possible,
        since the assets are in the possession of the clearing house.

        For the purposes of this paper it is more meaningful to use CSA agreements 
        where rehypothecation is allowed.
        Even though clearing through a CCP and trading under a CSA is very similar
        from a theoretical collateralization perspective,
        the lack of rehypothecation with a CCP is very restrictive.
        Hence, throughout the paper, CSA agreements will be mentioned the most,
        but the implication of using central clearing instead should also be clear.

    Many other forms of credit risk mitigation, than the ones mentioned here, exists. 
    Some derivatives contain break clauses that allow a party to prematurely terminate the 
    contract with a cash settlement corresponding to the derivative's value at that time.
    It is also possible for dealers to buy insurance against their counterparty's default,
    such that a notional amount is paid to the dealer if the counterparty defaults.
    The credit mitigations covered here are the ones deemed most relevant in studying funding costs.

    The following section briefly introduces some theory on interest rates,
    which will later be necessary to understand how funding value adjustments 
    came about in the first place.

\end{document}
        