% !TEX root = sub-main.tex
\documentclass[main.tex]{subfiles}

\begin{document}
    This section will provide an example of funding costs in a single-period model
    using a risk-free asset as the project under the firm's consideration.
    Consider the economy defined by a single-period model with $N=5$ states, 
    and the following associated Arrow-Debreu prices:
        \begin{table}[H]
            \centering
            \begin{tabular}{l|rrrrr}
                $i$ & 1 & 2 & 3 & 4 & 5 \\
                \hline
                $\psi_{i}$ & $\num{0.06}$ & $\num{0.24}$ & $\num{0.29}$ & $\num{0.28}$ & $\num{0.12}$ \\
            \end{tabular}
            \caption{}
            \label{tbl:example-firm-structure}
        \end{table}
    implying a discount factor of $\discountfactor = \num{0.99}$ and a risk-free interest rate of $\rfrate = \pct{0.010101}$.
    A firm operates in this economy and invests in risky assets 
    which are funded by equity and debt deposits and returns payoff specified shortly.
    In the event of default, the firm is assumed to face no distress cost, i.e. $\kappa = 1$, 
    such that the bankruptcy estate is distributed entirely to the creditors.
    The firm has been funded by debt such that the face value of debt is $\num{80}$, 
    which gives rise to the following payoff structure:
    \begin{table}[H]
        \centering
        \begin{tabular}{l|rrrrr}
            $i$ & 1 & 2 & 3 & 4 & 5 \\
            \hline
            $A(\omega_{i})$ & \num{120} & \num{110} & \num{100} & \num{95} & \num{60} \\
            $D(\omega_{i})$ & \num{80} & \num{80} & \num{80} & \num{80} & \num{60} \\
            $E(\omega_{i})$ & \num{40} & \num{30} & \num{20} & \num{15} & \num{0}
        \end{tabular}
        \caption{}
        \label{tbl:example-pre-project-capital-structure}
    \end{table}
    The associated present values of the payoffs, $A$, $D$ and $E$, 
    are discounted expected value of the payoff with respect to the risk-neutral probability measure:
        \begin{gather*}
            \pi(A) = \discountfactor \mathbb{E}^{\rnmeasure}\left[A\right] = \num{96.40} \\
            \pi(D) = \discountfactor \mathbb{E}^{\rnmeasure}\left[D\right] = \num{76.80}
            \qquad \pi(E) = \discountfactor \mathbb{E}^{\rnmeasure}\left[E\right] = \num{19.60}
        \end{gather*}
    The face value of the debt includes a credit spread that the firm must pay in order to account for its own credit risk.
    As seen in \cref{tbl:example-pre-project-capital-structure},
    the creditors do not receive their entire face value in the default event, $\omega_5$.
    The relative difference between the discounted payoff and the promised face value
    represents the credit spread of the creditors.
    If the creditors obtain the debt by paying the discounted payoff,
    the credit spread will ensure that the net present value of obtaining the debt is zero.
    In addition to calculating the shareholders' marginal valuation of a new project,
    it is interesting to also evaluate the impact on the creditors' valuation of their claim. 
    Therefore, it is useful to calculate the credit spread of the firm's debt 
    before entering any projects and the credit spread after entering a project.
    The same goes for the loss rate.

    The credit spread before entering into any projects is 
    $\num{80}/\num{76.80} - \grossrfrate = \pct{0.031565}$.
    Using \cref{eqn:creditor-loss-rate}, the loss rate of the creditors in the default event is:
    $\phi = (\num{80}-\num{60})/\num{80} = \pct{0.25}$
    while in all other states the loss rate is zero, as the firm does not default.

    The derivations in previous sections, 
    which described limiting spreads and marginal shareholder valuations, 
    were rooted in the assumption of the firm obtaining an infinitesimal project.
    This section will use the results in a practical application,
    where a larger than infinitesimal project will be obtained by the firm.
    All equations describing marginal shareholder valuations will still hold,
    as long as the project is not \textit{too large}.
    The project is not too large as long as its payoff and financing do not 
    alter the firm's default probability, which, in this discrete setting, means
    that the set of default and no-default states should remain unchanged.
    Such a project will be presented in the following paragraph.
    
    Assume that the firm faces a new risk-free project in which it can invest
    and that the project has a promised return of $\num{1}$ at time 1.
    The project is risk-free in the sense that the payoff is known with certainty at time 0, so:
        \begin{table}[H]
            \centering
            \begin{tabular}{l|rrrrr}
                $i$ & 1 & 2 & 3 & 4 & 5 \\
                \hline
                $Y(\omega_{i})$ & $\num{1}$ & $\num{1}$ & $\num{1}$ & $\num{1}$ & $\num{1}$
            \end{tabular}
            \caption{}
            \label{tbl:single-period-simple-derivative-payoff}
        \end{table}
    which implies a present value of 
    $\pi(Y) = \discountfactor \mathbb{E}^{\rnmeasure}\left[Y\right] = \num{0.99}$, 
    corresponding to the price of 1 zero coupon bond, 
    as the project is merely an investment in the risk-free asset.
    Obtaining the payoff requires an upfront cost equal to the fair value of the project.
    With a slightly redefined notation, since the project is not infinitesimal,
    the marginal investment cost of the project will be denoted by $u$.
    Assume that the counterparty offering the project makes a zero net present value investment, 
    such that the price of the project equals the value, i.e. $u = \pi(Y)$.
    As discussed in previous sections, the firm has different means of obtaining funding
    for paying the investment cost of the project.
    Financing through debt issuance is examined in the following section 
    and financing by share issuance in the section after that.

    \subparagraph{Digression on the limiting spread}
    As was calculated above, the limiting spread is equal to the credit spread of the existing debt.
    This is no coincidence, and this digression will explain why it is so,
    and what the implications are.
    Recall the definition of the limiting spread, repeated here for convenience:
        \begin{equation*}
            S
            =
            \frac{
                \mathbb{E}^{\rnmeasure}\left[\phi\right]
                \grossrfrate
            }{
                1
                -
                \mathbb{E}^{\rnmeasure}\left[\phi\right]
            }
        \end{equation*}
    The credit spread of existing debt can be calculated by dividing the face value of the debt
    with the present value of the debt claim and subtracting the gross risk free rate.
    Denote the face value by $F$. 
    The present value of the debt claim is the discounted face value, $\discountfactor F$,
    adjusted for the credit risk. 
    The credit value adjustment as usual corresponds to the discounted expected value of
    the positive exposure, $F$, multiplied by the loss given default, $\phi$.
    Hence the credit spread of existing debt is given by:
        \begin{equation*}
            \frac{
                F
            }{
                \discountfactor F
                -
                \discountfactor
                \mathbb{E}^{\rnmeasure}\left[
                    F \phi
                \right] 
            } 
            -
            \grossrfrate
            =
            R \left(
            \frac{
                1
            }{
                    1
                    -
                    \mathbb{E}^{\rnmeasure}\left[
                        \phi
                    \right] 
            } 
            - 
            1
            \right)
            =
            \frac{
                \mathbb{E}^{\rnmeasure}\left[\phi\right]
                \grossrfrate
            }{
                1
                -
                \mathbb{E}^{\rnmeasure}\left[\phi\right]
            }
        \end{equation*}
        Which can be recognized as the limiting spread. 
        Hence, the definitions of the marginal shareholder valuations are based on
        the assumption that the post-project credit spread 
        will equal the pre-project credit spread.
        However, these definitions are derived using infinitesimal projects. 
        In practical applications,
        it would therefore be more appropriate to refer to the limiting spread as an approximation 
        of the credit spread after obtaining a larger-than-infinitesimal project.
        The mathematics have been accounted for, 
        but the approximation does seem to be financial sound as well.
        First of all, the post-project credit spread are based on the the risk of the entire firm,
        which most likely encompasses many projects.
        Each new project is therefore going to be of relatively small size compared
        to the entire firm, and it will only have a small effect on the overall riskiness.
        Second, this effect is enhanced if the firm mostly invests in projects that matches
        its overall riskiness in the first place.
        Third and last, as was mentioned earlier, according to \textcite{Castagna2012FVA},
        the cost of capital will only gradually update, 
        such that obtaining a new project only have a very marginal effect on the credit spread.

        In conclusion, the limiting spread is not merely a mathematical result
        but also a financially sound approximation of the incremental cost of obtaining new projects.

\end{document}