% !TEX root = ./sub-main.tex
\documentclass[main.tex]{subfiles}

\begin{document}
    \subsection{Credit Value Adjustments}
        A Credit Value Adjustment, \CVA/, is the price that a dealer is willing to pay 
        to hedge the counterparty credit risk of a financial instrument.
        This concept is best introduced by an example. 
        
        \begin{example}
        Suppose a credit risk-free dealer that has obtained market risk 
        which she wants to hedge by buying an OTC derivative.
        The derivative is offered by two different banks and the dealer can buy from either.
        One bank has a high credit rating, say AAA, and the other has a slightly lower credit rating, say BBB. 
        The two banks offer the same derivative, except from the fact that their credit ratings differs.
        Thus, in one case the dealer's counterparty is rated AAA and in the other case the counterparty is rated BBB;
        so, if the banks offer the product at the same price, 
        the dealer is clearly going to prefer doing business with the bank rated AAA.

        Since the BBB rated bank wants to be competitive and win the deal,
        it is going to submit a lower ask on the derivative than its competitor.
        If the BBB rated bank continues to lower the price, 
        at some point the dealer will be indifferent between buying 
        from the AAA rated bank and the BBB rated bank.
        At this price, the BBB rated bank have sufficiently compensated the dealer for taking on the additional credit risk;
        the discount offered by the BBB rated bank, 
        is exactly the value that the dealer attributes to the additional credit risk. 
        This value is the \CVA/.

        This motivates the definition of \CVA/ as the difference between the price of the instrument 
        including counterparty credit risk and the price of the instrument excluding counterparty credit risk.
        \end{example}

        From this example, it is clear that the credit risk of the BBB rated bank contributes to the \CVA/
        when the dealer calculates it.
        This principle can be extended further.
        In a transaction with two counterparties there might also be two sources of credit risk;
        so, suppose now that the dealer's institution is not credit risk-free 
        but has a relatively low credit rating.
        Also, refer to the BBB rated bank as the counterparty of the dealer.
        The side from which \CVA/ is considered is not unimportant,
        and if the counterparty calculated the trade's \CVA/, it would account for the credit risk of the dealer.
        To not get lost in the terms, say that the dealer calculates $\CVA/_{F}$ 
        and that the counterparty calculates $\CVA/_{C}$.

        While $\CVA/_{F}$ is a negative contributor to the derivative's value perceived by the dealer, 
        as it turns out, $\CVA/_{C}$ is a benefit.
        If the dealer has outstanding liabilities with her counterparty
        and she defaults, she will not be able to fully pay her obligations. 
        Surely, this possibility of receiving a lower payment is what the counterparty accounts for 
        by calculating and applying $\CVA/_{C}$.
        However, from the dealer's point of view this is a possibility of having to pay a lower amount,
        which is a benefit to her that should increase the amount she is willing to pay.
        This increase in the perceived value of the derivative, 
        stemming from the dealer's own possibility of defaulting, 
        is referred to as the \DVA/.

        Say that the dealer calculates $\DVA/_{F}$ and the counterparty calculates $\DVA/_{C}$.
        Since both $\DVA/_{F}$ and $\CVA/_{C}$ are concerned with the default risk of the dealer,
        and vice versa for $\DVA/_{C}$ and $\CVA/_{F}$, in theory, the following symmetric relations hold:
            \begin{align*}
                \CVA/_{F} &= \DVA/_{C} \\
                \DVA/_{F} &= \CVA/_{C}
            \end{align*}
        These relations simply state the fact that
        the price of the counterparty credit risk experienced by the dealer,
        is equal to the price of the counterparty credit risk as experienced by the counterparty itself, and vice versa.
        Including both the \CVA/ and the \DVA/ is referred to as a bilateral adjustment,
        as opposed to a unilateral, where only the \CVA/ is included.
        According to the symmetry above,
        both parties can agree on the necessary credit valuation adjustment in a bilateral setting,
        since each party is also calculating the counterparty's \CVA/ and \DVA/, however with the labels switched.
        To this extent, the parties will reach symmetric valuations of the financial instrument. 
        This result is however merely theoretical; 
        in practice each institution will apply different \CVA/ models
        and be operating under different accounting rules, 
        which will inevitably lead to the parties reaching different adjustments. 
        
        Eliminating \CVA/ and \DVA/ is possible by hedging the credit exposure due to the instrument,
        which is possible with a collateralization scheme. 
        Perfect collateralization would ensure no credit exposure,
        however even strong CSA agreements will have collateral calls happening less frequently
        than what would be necessary to obtain perfect collateralization.
        Still CSA agreements will reduce the credit exposure and hence \CVA/ and \DVA/.

\end{document}
        