% !TEX root = ./sub-main.tex
\documentclass[main.tex]{subfiles}

\begin{document}
    \FVA/ is closely related to \DVA/ in the sense that the quantity they represents have potential overlaps.
    If these overlaps are not carefully considered, they might lead to so called \textit{double counting}
    which refers to the action of performing, at least a part of, a valuation adjustment twice. 
    Clearly, this can lead to both over- or underpricing of assets.
    This section covers the overlap between the \FVA/ and parts of the \DVA/.

    For this purpose it is useful to separate the factors that contributes to the \DVA/,
    meaning the sources of \DVA/. 
    A firm defaults if it is not able to meet its liabilities;
    the possibility of defaulting on each liability contribute to the \DVA/.
    Let $\DVA/_{\text{derivatives}}$ refer to the value arising
    because the firm might default on its derivative obligations,
    and let $\DVA/_{\text{funding}}$ refer to the value arising 
    because it might default on the funding required for the derivative portfolio.

    Assume that the entire credit spread is compensation for default risk.
    Then the \FBA/ is exactly equal to $\DVA/_{\text{funding}}$. 

    The CDS credit spread reflects how much the seller of the CDS must receive from the buyer
    to compensate for the probability that the seller must pay the notional if the underlying firm defaults.
    The funding spread reflects how much the funding institution must receive from the firm 
    to compensate for the probability that the firm does not repay its debt, 
    i.e. the funding institution loses the notional.
    Usually the funding spread and the CDS credit spread are different due to a credit liquidity premium,
    but imagine an ideal world with no friction, i.e. infinite information, infinite liquidity, 
    instantaneous price updates that reflect all available information, etc.
    From the previous definitions, it can be seen that in this ideal world
    the CDS credit spread of each firm is going to be the same 
    as the spread the firm pays on unsecured financing, i.e. its funding spread.

    The CDS credit spread is an input in $\CVA/_{C}$ and therefore also in $\DVA/_{F}$.
    But, if the CDS credit spread and the funding spread is identical, $\DVA/_{F}$ can be interpreted differently;
    namely, the cost to the firm of ensuring that it does not default, as evident from the following example.
    If the firm wants to make sure it does not default,
    it can borrow today its future expected liabilities and put them aside.
    Whenever a liability matures, the firm uses cash from this pool of money to cover the debt.
    For borrowing the pool of money, the firm pays the interest of unsecured loans, i.e. its cost of funding.
    However, the firm should always be able to pay its liabilities,
    and, by setting aside these funds, the firm has essentially hedged its own default. 
    This thought example should show that \DVA/ is related to \FVA/ through the funding costs.
    
    If \DVA/ and \FVA/ are related, it would seem like there might be an overlap between the two,
    such that accounting for both in the valuation of a derivative leads to a double-counting.
    However, according to \textcite{Ruiz2015XVA}, 
    this would be a misunderstanding of how \DVA/ and \FVA/ occurs in reality.
    Suppose a firm with default risk as well as multiple derivatives and counterparties.
    Without changing the conclusion of the following the liquidity premium can be assumed to be zero, 
    such that the firm's CDS credit spread is identical to its funding spread.
    The firm's \DVA/ is the aggregated cost, paid by counterparties,
    of hedging the counterparties credit risk to the firm.
    As already mentioned, this can be seen as the firm's own funding costs
    if the firm managed its own default risk by borrowing today all future liabilities.
    However, in reality that would not be an actual cost that the firm face,
    since it would not manage its own default risk in that manner.
    To actually account for its own credit risk in the valuation process,
    the firm should consider what it itself actually does to manage it,
    and not what counterparties do or what it would have done in an ideal world.

    First, \DVA/ does not account for any funding benefits due to inter-netting sets.
    Rather it considers each netting set separately, by representing the cost 
    of borrowing funds today to meet the future liability of each and every netting set.
    In addition, to manage their own credit risk, firms cover future liabilities
    by hedging and posting collateral.
    The firms attempts to align future cash flows to offset each other
    and potential mismatches are covered by posting initial margins. 
    Hedging and collateralization has a cost; 
    the present value of that cost is the \FVA/.

    Hence, it would be wrong to refer to \DVA/ as the firm's cost of funding.
    It is the cost to the counterparties of managing their credit risk to the firm,
    which they can hedge by buying CDS contracts,
    but the cost to the firm of managing its own risk is very different. 
    The firm manages its own credit risk by hedging and collateralization.

    When a firm needs to value a derivative it should evaluate the actual costs that it will be facing.
    It must consider netting benefits, funding surpluses due to mismatches in cash flows,
    as well as costs due to initial margin.

\end{document}
        