% !TEX root = ./sub-main.tex
\documentclass[main.tex]{subfiles}

\begin{document}
    \section{Quantifying Funding Costs}
    \subsection{A Dealer in a Multi-Period Economy}
    \label{sec:swap-examples}
        This section aims to illustrate
        how the funding costs and benefits of a multi-period swap contract
        can be described by a simple economical setup.
        The examples will be based on the two results derived in the previous sections,
        namely the shareholders' marginal valuation of both an unsecured swap as well as a secured hedging swap.
        As opposed to the single-period model analysed in \cref{sec:single-period-model},
        different fundamental values in this \namecref{sec:swap-examples} will have a probability of changing over time.
        The values in reference are specifically
        the risk-free rate,
        the swap market value,
        and of course the swap floating rate.
        
        Maintaining the purpose of analysing funding implications,
        the possible states are now represented by a binomial tree.
        At the interim date, the two possible states are denoted by $\omega_\mathscr{u}$ and $\omega_\mathscr{d}$.
        Correspondingly, at the maturity date the two possible states are either
        $\omega_{\mathscr{u},\mathscr{u}}$ and $\omega_{\mathscr{u},\mathscr{d}}$,
        or $\omega_{\mathscr{d},\mathscr{u}}$ and $\omega_{\mathscr{d},\mathscr{d}}$,
        depending on the asset value going up or down in the first time period respectively.
        \\
        In the state $\omega_{\mathscr{d},\mathscr{d}}$, the liabilities exceed the asset value,
        and the dealer defaults.
        In this case the shareholders receive a payoff of 0.
        \\
        The asset value structure is illustrated in 
        \cref{fig:example-asset-value-multi-period-dealer}.
        Each period the asset values are assumed to either increase with a factor $\mathscr{u} = 1.1$
        or decrease with a factor $\mathscr{d} = 0.85$.
        The asset values are determined under the risk-neutral measure,
        such that at each point in time the value is equal to the expected discounted value of the next period.
        By that definition, and by a short-term risk-free rate assumed to be $r_{0,1}=2\%$ at the inception date,
        the probability of being in the up-state at the interim date is calculated as:
        \begin{equation*}
            p_{\mathscr{u}}^{0} =
            \frac{
                1 + 2\% - 0.85
            }{
                1.1 - 0.85
            }
            = \num{0.68}
        \end{equation*}
        And consequently, $p_{\mathscr{d}}^{0} = 1 - p_{\mathscr{u}}^{0} = \num{0.32}$.
        Moving to the up-state from time 1 has a probability of
        $p^1_\mathscr{u}=(1+r_{1,2}-0.85)/(1.1-0.85) = \num{0.696016}$.

        The long-term risk-free discount rate from time 0 to time 2 is assumed to be $r_{0,2}=2.2\%$.
        To determine the expected short-term rate at the interim date, the forward rate is calculated:
        \begin{equation*}
            r_{1,2} =
                \frac{
                    \left(1 + 2.2\%\right)^{2}
                }{
                    1 + 2\%
                }
            - 1
            = 2.4\%
        \end{equation*}
        
        The risk-neutral probabilities of moving to the three different states at the maturity date are calculated as:
        \begin{align*}
            p_{\mathscr{u},\mathscr{u}}
            &=
            % p_{\mathscr{u}}
            % \frac{
            %     1 + 2.4\% - 0.85
            % }{
            %     1.1 - 0.85
            % }
            % =
            \num{0.473291}
            \\
            p_{\mathscr{u},\mathscr{d}} +
            p_{\mathscr{d},\mathscr{u}}
            &=
            % p_{\mathscr{d}}
            % \frac{
            %     1 + 2.4\% - 0.85
            % }{
            %     1.1 - 0.85
            % }
            % +
            % p_{\mathscr{u}}
            % \frac{
            %     1.1 - (1 + 2.4\%)
            % }{
            %     1.1 - 0.85
            % }
            % =
            \num{0.429434}
            \\
            p_{\mathscr{d},\mathscr{d}}
            &=
            % p_{\mathscr{d}}
            % \frac{
            %     1.1 - (1 + 2.4\%)
            % }{
            %     1.1 - 0.85
            % }
            % =
            \num{0.097275}
        \end{align*}

        At the interim date, the dealer's creditors have a known claim of $L_{1} = 10$,
        meaning $W=10(1+r_{1,2})=\num{10.240039}$.
        Meanwhile, the long-term liabilities, which are also known with certainty, are $L_{2} = 70$.
        The dividend paid to the shareholders at the interim date is $\theta_1 = 0$, and there are no distress costs.
        As mentioned above, the asset value does not cover the total liabilities at state $\omega_{\mathscr{d},\mathscr{d}}$ as $72.25 < L_{2} + W$,
        hence the dealer defaults.
        \\
        The short-term liabilities are, on the other hand, not large enough to trigger a default at the interim date
        regardless of the state outcome.

        \begin{figure}[H]
            \centering
            \begin{tikzpicture}[>=stealth,sloped]
                \matrix (tree) [
                  matrix of nodes,
                  minimum size=1cm,
                  column sep=3.5cm,
                  row sep=0.85cm,
                ]
                {
                &               & $\mathscr{u}^{2}A_{0}=121$ \\
                & $\mathscr{u}A_{0} = 110$ & \\
    $A_0 = 100$ &               & $\mathscr{u}\mathscr{d}A_{0}=93.5$ \\
                & $\mathscr{d}A_{0} = 85$  & \\
                &               & $\mathscr{d}^{2}A_{0}=72.25$ \\
                };
                \draw[->] (tree-3-1) -- (tree-2-2) node [midway,above] {\tiny
                $p_{\mathscr{u}}=\num{0.68}$};
                \draw[->] (tree-3-1) -- (tree-4-2) node [midway,below] {\tiny
                $p_{\mathscr{d}}=\num{0.32}$};
                \draw[->] (tree-2-2) -- (tree-1-3) node [midway,above] {\tiny
                $p_{\mathscr{u},\mathscr{u}}=\num{0.473291}$};
                \draw[->] (tree-2-2) -- (tree-3-3) node [midway,below] {\tiny
                $p_{\mathscr{u},\mathscr{d}}=\num{0.206709}$};
                \draw[->] (tree-4-2) -- (tree-3-3) node [midway,above] {\tiny
                $p_{\mathscr{d},\mathscr{u}}=\num{0.222725}$};
                \draw[->] (tree-4-2) -- (tree-5-3) node [midway,below] {\tiny
                $p_{\mathscr{d},\mathscr{d}}=\num{0.097275}$};
            \end{tikzpicture}
            \caption{The asset value of the dealer in each time period.}
            \label{fig:example-asset-value-multi-period-dealer}
        \end{figure}

        Having defined the setup of the dealer's capital structure,
        a swap contract is now introduced between the dealer and a counterparty.
        For simplicity, the counterparty is assumed to have no credit-risk.
        The swap will have a relatively small notional payoff to the extend
        that it does not affect the default- and no-default states of the dealer.

        The first example will apply the theory from \cref{sec:unsecured-swap-valuation}
        to find the shareholders' valuation of the project being entered.
        In the second example, the dealer additionally hedges the swap's market risk 
        by trading the opposite position in an exchange.
        The original trade will be unsecured 
        while the hedge will be traded under a collateralization agreement,
        which allows for the theory discussed in \cref{sec:secured-swap-valuation} to be applied.

        \subsection{Example of unsecured swap}
            Suppose the dealer enters a swap contract with the credit risk-free counterparty.
            She pays a constant fixed leg $K=\num{1}$ to the counterparty at each time period.
            Correspondingly, at each time period,
            the dealer receives a random floating leg, $X_t$, from the counterparty.

            Since the counterparty is credit-risk free,
            the dealer can always expect to receive the full contractual amount of the floating leg.
            Therefore, there is no \CVA/ and
            the difference between the risk-free value and the credit risk adjusted price is the \DVA/.

            The floating legs can take on any amount within reason,
            such that the cash flows at each time period are random.
            However, the market neutral expected cash flows are known
            by both the dealer and the counterparty.
            If the dealer's swap leg has a higher value than the counterparty's,
            she will have to pay an upfront price to the counterparty,
            and vice versa.

            The time 0 expected payments of the swap contract are summarized in \cref{tbl:swap-legs}.
            Notice, that at the interim date the dealer expects a positive cash flow of
            $\mathbb{E}_{0}^{\rnmeasure}\left[\mathcal{C}_1\right] = \mathbb{E}_{0}^{\rnmeasure}\left[X_1 - K\right] = \num{0.2}$,
            which will be used for retiring existing debt.
            The expected cash flow at time 2 does not change over time.

            At the maturity date the dealer liquidates all of her assets,
            which she uses to pay the remaining outstanding amounts.
            Additionally, the existing creditors' liabilities are assumed to rank pari passu with the counterparty's contingent liabilities.
            \\
            Since the expected discounted market value of the floating payments is largest,
            the dealer seems to be obliged to pay the counterparty an upfront price.
            As per the Modigliani-Miller proposition, 
            a zero net present value investment leaves the aggregate wealth unchanged.
            For this to be applicable, the price of the swap must also account for the dealer's own default risk,
            i.e. include the aforementioned \DVA/.
            Otherwise, it cannot be a zero net present value investment for both the dealer and the counterparty.
            
            \begin{table}[H]
                \centering
                \begin{tabular}{l|rr||r}
                    $t$ & 1 & 2 & Present value \\
                    \hline
                    \rule{0pt}{1.1em}
                    $\mathbb{E}_{0}^{\rnmeasure}\left[K\right]$ & $\num{1}$ & $\num{1}$ & $\num{1.937802706}$ \\
                    \rule{0pt}{1.1em}
                    $\mathbb{E}_{0}^{\rnmeasure}\left[X_t\right]$ & $\num{1.2}$ & $\num{0.95}$ & $\num{2.08601}$ \\
                    \rule{0pt}{1.1em}
                    $\mathbb{E}_{0}^{\rnmeasure}\left[\mathcal{C}_t\right]$ & $\num{0.2}$ & $\num{-0.05}$ & $\num{0.1482079039}$ \\
                \end{tabular}
                \caption{}
                \label{tbl:swap-legs}
            \end{table}

            When defaulting at time 2, i.e. in state $\omega_{\mathscr{d},\mathscr{d}})$,
            the dealer's total liabilities are calculated as:
            \begin{align*}
                \mathbb{E}_{0}^{\rnmeasure}\left[
                    (1-\phi(\omega_{\mathscr{d},\mathscr{d}}))\left(
                        L_{2} - 
                        \mathcal{C}_{1}R_{1}
                        - \mathcal{C}_2
                    \right)
                \right]
                &=
                (1-\phi(\omega_{\mathscr{d},\mathscr{d}}))\left(\num{70} - \num{0.2}R_{1} + \num{0.05}\right)\\
                &=
                (1-\phi(\omega_{\mathscr{d},\mathscr{d}}))\num{69.8452}
            \end{align*}
            And by definition, this amount is equal to the total remaining asset value.
            Remember that at time 2 the dealer has already paid the liabilities due at the interim date.
            To find the price of the project
            as well as the loss rate given default after obtaining the project,
            the following system of equations must be solved for $u$ and $\phi(\omega_{\mathscr{d},\mathscr{d}})$:
            \begin{align}
                &\left\{\begin{array}{@{}l@{}}
                    \mathscr{d}^{2}A_{0} - \left(W+\mathbb{E}_{1}^{\rnmeasure}\right)
                    =
                    \mathbb{E}_{0}^{\rnmeasure}\left[
                        (1-\phi(\omega_{\mathscr{d},\mathscr{d}}))\left(L_{2} - 
                        \mathcal{C}_{1}R_{1}
                        - \mathcal{C}_2\right)
                    \right]
                    \\
                    u =
                    \mathbb{E}_{0}^{\rnmeasure}\left[
                        \delta_{1}(X_1-K_1)+(\delta_{2}(X_2-K_2(1-\phi)))
                    \right]
                \end{array}\right.
                \label{eqn:swap-example-equation-system}
                \\[1.1em]
                \Leftrightarrow
                \qquad
                &\left\{\begin{array}{@{}l@{}}
                    \displaystyle
                    \num{72.25} - \num{10.24}
                    =
                    (1-\phi)\num{69.8452}
                    \\
                    \displaystyle
                    u =
                    \delta_2\left(
                        \num{0.1482079039}(1-\phi)p_{\mathscr{d},\mathscr{d}}
                        +
                        \num{0.1482079039}\left(1-p_{\mathscr{d},\mathscr{d}}\right)
                    \right)
                \end{array}\right.
                \nonumber
            \end{align}
            The first equation in \cref{eqn:swap-example-equation-system} assures that the creditors receive the entire asset base if the firm defaults.
            The second equation sets the price of the swap as the discounted expected payoff.
            Solving this equation system yields a market neutral swap price of $u=\num{0.158655}$,
            and a loss rate in the default state of 
            $\phi(\omega_{\mathscr{d},\mathscr{d}})=\pct{0.112180}$.
            Using the loss rate, the value of the legacy creditors' long term claim can be calculated.
            At time 2 the payoff in the default state is 
            $L_{2}*(1-\phi(\omega_{\mathscr{d},\mathscr{d}})) = \num{62.14739601}$.
            At time 1 the expected value of the claim is therefore \num{67.61315718},
            and at time 0 the value is \num{66.287413}.

            The credit spread in each period is the debt's no-default value one period ahead
            divided by its current value less the risk-free rate.
            Hence the post-project actual credit spreads for time 0 and time 1 is:
            \begin{align}
                S_{0} 
                &=
                \frac{
                    \num{67.61791744}
                }{
                    \num{66.29207592}
                }
                -
                R_{0}
                =
                \pct{0}
                \\
                S_{1} 
                &= 
                \frac{
                    \num{70}
                }{
                    \num{67.61791744}
                } 
                -
                R_{1}
                =
                \pct{0.0112246}
            \end{align}
            Since the dealer cannot default at time 1,
            the upfront price can be funded with short-term debt paying 0 credit spread.
            If the firm were to pay a spread on the short-term debt starting at time 0,
            this would be subtracted from the liquidated asset value. 

            By using the risk-neutral marginal market valuation of the swap contract
            defined in \cref{eqn:swap-value-multi-period},
            the \DVA/ can then be computed as:
            \begin{align}
                \DVA/ &= u - V_{rf}
                \nonumber
                \\
                &= u - \mathbb{E}_{0}^{\rnmeasure}\left[\sum_{t=1}^{2}\delta_t \mathcal{C}_t\right]
                = \num{0.0104476}
            \end{align}

            Turning to the shareholder valuation of the project.
            Cash flows from the swap contract may have an impact on the shareholders' valuation of the project.
            Since the swap's price is its risk-neutral value adjusted for credit risk,
            the project is a zero net present value investment for the counterparty.
            If a wealth transfer has happened, it is bound to be between the shareholders and the long-term creditors.

            The swap provides an overall funding benefit for the dealer,
            and increases the value of the shareholders' claim.
            Since the dealer cannot default at the interim date,
            there are no funding costs from obtaining short-term debt at time 0.
            At time 2, the dealer expects a swap payment from the counterparty,
            and this cash flow is passed on to the creditors, reducing the long-term debt.
            Hence, the shareholders do not have to pay interest on this retired debt,
            and their payoff increases.
            
            With $\mathbb{E}_{t}\left[\mathcal{C}_1\right]=\num{0.2}$,
            $\mathbb{E}_{t}\left[\mathcal{C}_2\right]=\num{-0.05}$,
            $u=\num{0.158655}$,
            and the assumption that the counterparty is credit risk-free,
            the total impact on the shareholders' benefit is calculated using \cref{eqn:shareholders-value-multi-period-swap}:
            \begin{equation}
                G_{swap} = \num{-0.00906097}
            \end{equation}
            This value suggests a wealth transfer of $\num{-0.00906097}$
            between the shareholders and the creditors of the long-term debt,
            such that the project is a negative net present value investment for the creditors.

            The price that would make this project a zero net present value investment for the shareholders,
            is found by fixing $G_{swap}$ to 0,
            and solving for $u^{\ast}$.
            The difference between the market neutral credit risk adjusted price and $u^{\ast}$ is then the \FVA/:
            \begin{equation}
                G_{swap} = 0
            \end{equation}
            yielding a funding adjusted price of $u^{\ast} = \num{0.148727}$.
            \\
            The donation from the counterparty required is then:
            \begin{equation}
                \FVA/ = u^{\ast} - u = \num{-0.00992852}
            \end{equation}

            The project's positive impact on the shareholders' wealth is an of expression of the limited funding costs
            that the dealer faces in this setup.
            In the next section the example is extended to include a fully collateralized hedged position.
            The margin requirements will then potentially imply an exposure to funding costs or funding benefits.

        \subsection{Example of secured hedging swap}
            Suppose that the dealer enters the same swap contract with the same counterparty as described above.
            Additionally, she hedges the swap contract by entering the opposite position with a hedging dealer
            where she pays the floating leg.
            The dealer and the hedging dealer have in place a CSA agreement 
            requiring full collateralization, i.e. with no thresholds or minimum transfer amounts.
            Besides the variation margin,
            the CSA requires an initial margin of 50\% of the swap's price.
            The initial margin is posted both at the inception date and the interim date.
            Corresponding to the dealer, the hedging dealer is assumed credit risk-free at the interim date.

            Assume that the swap contract's price equals its credit risk adjusted value.
            With the hedge transaction included,
            the dealer's portfolio is free of market risk,
            and all outgoing cash flows from the swap's interest payments
            are perfectly offset by an incoming cash flow.
            The dealer must however fund the margin requirements by obtaining new short-term debt,
            and similarly, she uses the received margin postings to retire existing debt.
            \\
            The specific required margin postings are summarized in \cref{tbl:swap-margin-postings}.

            \begin{table}[H]
                \centering
                \begin{tabular}{l|rr}
                    $t$ & 0 & 1 \\
                    \hline
                    \rule{0pt}{1.3em}
                    $\mathbb{E}_{0}^{\rnmeasure}\left[M_t\right]$ & $\tilde{u}$ & $\frac{1}{1+r_{1,2}}\mathbb{E}_{1}^{\rnmeasure}\left[\mathcal{C}_{2}\right]$ \\
                    \rule{0pt}{1.3em}
                    $\mathbb{E}_{0}^{\rnmeasure}\left[I_t\right]$ & $\frac{1}{2}\tilde{u}$ & $\frac{1}{2}\frac{1}{1+r_{1,2}}\mathbb{E}_{1}^{\rnmeasure}\left[\mathcal{C}_{2}\right]$ \\
                \end{tabular}
                \caption{
                    Expected collateral payments. 
                    Positive amounts will be collateral calls from the hedge dealer,
                    negative amounts from the dealer herself.
                }
                \label{tbl:swap-margin-postings}
            \end{table}

            As in the previous section, the dealer cannot default at time 1,
            hence no credit spread is paid for the short-term loans at time 0.
            Posting collateral increases the asset value,
            and financing it increases the short-term liabilities.
            When the dealer receives back the forward discounted collateral,
            she then uses it to pay the debt with the exact amount at the interim date.
            \\
            The dealer will not have any contingent liabilities due to the swap payments at the maturity date.
            The collateral received (posted) at the interim date will be paid (received) back at the maturity date.
            As a result of that,
            the liabilities at time 2 has both increased and decreased with the margin requirements at time 1.
            If defaulting, the dealer's creditors will have a total payoff calculated as:
            \begin{align}
                \mathbb{E}_{0}^{\rnmeasure}\left[
                    (1-\phi(\omega_{\mathscr{d},\mathscr{d}}))\left(
                        L_{2}
                        -(M_1+I_1)R_{1}
                        +(M_1+I_1)R_{1}
                    \right)
                \right] 
                &= (1-\phi(\omega_{\mathscr{d},\mathscr{d}}))\num{70}
            \end{align}
            The short-term debt is paid at the interim date with liquidated assets.
            If there is a difference in price between the two swap contracts,
            this will either increase or reduce the amount due,
            depending on which swap is more expensive.
            The total asset base at the default event will then have to account for covering this amount. 

            To find the market neutral credit risk adjusted price of the project, $u$, 
            as well as the loss rate given default, $\phi(\omega_{\mathscr{d},\mathscr{d}})$,
            the following equation system must be solved.
            \begin{equation}
                \left\{\begin{array}{@{}l@{}}
                    \mathscr{d}^{2} A - W - (\tilde{u}-u)R_{0}R_{1}
                    =
                    (1-\phi(\omega_{\mathscr{d},\mathscr{d}}))\num{70}
                    \\
                    u =
                    \mathbb{E}_{0}^{\rnmeasure}\left[
                        \delta_{1}(X_1-K_1)+(\delta_{2}(X_2-K_2(1-\phi)))
                    \right]
                \end{array}\right.
            \end{equation}
            As in the example with the unsecured swap the first equation ensures
            that the entire asset value amount is distributed to the creditors in a default.
            The price of the secured swap, $\tilde{u}$, is perceived as the credit-risk free expected discounted cash-flows.
            The second equation again sets the price as the discounted expected cash flows.
            \\
            By solving, a new loss rate of $\phi = \pct{0.11423357857841265}$ is obtained.
            The new swap price is computed as $u=\num{0.15425039456453227}$,
            which is slightly smaller than in the previous example,
            since the counterparty now trades with a marginally more secured dealer.

            With the long-term debt creditors' expected payoff at time 1 calculated as $\num{67.60088401}$,
            the credit spread at time 1 is given by:
            \begin{equation}
                S_1 =
                \frac{
                    \num{70}
                }{
                    \num{67.59950202}
                }
                - R_{1}
                \nonumber
                = \pct{0.01150666521}
            \end{equation}
            The credit spread at time 0 is 0,
            as the dealer cannot default at the interim date.
            
            Finally, the shareholders' valuation of the project is analysed.
            As the project is priced to be a zero net present value investment for the counterparty,
            a potential change of wealth must again be between the dealer's creditors and shareholders.
            The shareholders' change of wealth is computed the derived expression in \cref{eqn:shareholder-valuation-swap-hedged}.
            This derivation includes the extension of the fully collateralized hedged position.
            \\
            With the above computed credit spreads, and $u=\num{0.15425039456453227}$
            the shareholders' marginal valuation of entering the swap contract is calculated as:
            \begin{equation}
                G_{\text{swap,hedged}} = \num{-0.00994871}
            \end{equation}
            suggesting a negative net present value investment for the shareholders. 
            The price that makes the shareholders indifferent of entering the project, $u^{\ast}$, is then defined by fixing $G_{\text{swap,hedged}}$ to 0.
            This implies:
            \begin{equation}
                u^{\ast} = \num{0.1486201204475151}
            \end{equation}
            and an \FVA/ defined as:
            \begin{equation}
                \FVA/ = u^{\ast} - u = \num{-0.00563027}
            \end{equation}
            Hence the donation required of the counterparty is \num{-0.00563027},
            meaning the dealer would pay less than the original swap price.
            Seemingly, this would result in a negative net present value investment for the counterparty,
            and whether they have incentives to enter the funding value adjusted project remains indeterminate.
            
\end{document}