% !TEX root = ./sub-main.tex
\documentclass[main.tex]{subfiles}

\begin{document}
    \section{The origin of Funding Value Adjustments}
        Before the financial crisis of 2008, the spreads on CDS contracts referencing banks were very low.
        The differences between yields on highly secure government bond, such as T-Bills,
        and the interbank lending rates, e.g. LIBOR, were very low.
        As banks were considered almost risk-free, 
        they could all fund themselves at the interbank lending rates implied by LIBOR, Euribor, etc.
        Banks were seemingly similar to each other in this respect, 
        and the notion of a financial product's fair value was very much driving the pricing of derivatives issued by banks,
        since mispricing would lead to arbitrage opportunities.
        If one bank offered a financial contract at a lower price than a financial contract with identical terms
        offered by another bank, arbitrageurs would exploit this apparent mispricing. 
        The fact that banks contained more risk than perceived became clear in 2008
        with the failure of some large banks, 
        especially the bankruptcy of the investment bank Lehmann Brothers.
        These defaults made it clear that banks were in fact not risk-free; 
        firms financing banks needed to do so only when receiving an even larger credit spread,
        i.e. a lending rate exceeding the interest rate that was considered risk-free. 
        
        As a consequence, banks are now forced to pay additional interest on their funding, 
        which depends on their perceived default intensity.
        Due to the varying investment- and risk profiles of banks, 
        the perceived default intensity differs between them, 
        and each bank might face completely different funding schemes and costs than its competitors.
        Differing funding costs have massively challenged the concept of a derivative's fair value,
        since the price that different banks are willing to bid or offer might vary significantly. 
        This has lead many institutions to systematically applying adjustments to their prices
        in order to accommodate their funding costs; 
        adjustments that are aptly named Funding Value Adjustments. 
        This practice is condemned by some theoreticians, 
        which has ensued heavy debate.
        
        In the following section the circumstances under which funding costs arise will be explored.
        This precedes diving into the implications of differing funding costs, or the lack thereof,
        and the discussion of whether applying \FVA/s is even appropriate.

\end{document}
        