% !TEX root = sub-main.tex
\documentclass[main.tex]{subfiles}

\begin{document}
    \subsubsection{Funding by Existing Cash}
        Instead of relying on external resources to fund the project,
        the firm might be in an excess of cash that can be used for financing.
        If the firm finances the new project with cash from its balance sheet, 
        the equity increases by the present value of the expected payoff,
        offset by the upfront cost, and the cost of tying up capital in the project.
        The latter is an opportunity cost, since it locks capital
        that could otherwise have been invested in bonds earning the risk-free rate.
        The firm therefore has to pay its liabilities with an asset base that is
        reduced by the upfront price appreciated by the risk-free rate.
        Hence, the default event is:
            \begin{equation*}
                \mathcal{D}(q)
                = 
                \{
                    A - U(q)R + qY < L
                \}
            \end{equation*}
        and the marginal increase in the equity valuation per unit investment is:
            \begin{equation*}
                G_{\text{cash}} =
                    \left.
                    \frac{\partial }{\partial q} 
                    \discountfactor
                    \frac{
                        \mathbb{E}^{\mathbb{Q}}\left[
                            \left(
                                A - U(q)R + qY - L
                            \right)^{+}
                        \right] 
                    }{
                        q
                    } 
                    \right\rvert_{q=0}
            \end{equation*}
        This derivative is, again, very similar to the derivatives already examined,
        so, for brevity, the calculations in this section will be omitted.
        The marginal shareholder valuation of funding a project with existing cash can be reformulated as the following:
            \begin{align}
                G_{\text{cash}} &=
                    \discountfactor
                    \mathbb{E}^{\mathbb{Q}}\left[
                        \mathbbm{1}_{\mathcal{D}^{c}} Y
                    \right]
                    -
                    u
                    \mathbb{E}\left[\mathbbm{1}_{\mathcal{D}^{c}} \right]
                    \nonumber \\
                &=
                    \discountfactor
                    \mathbb{E}^{\mathbb{Q}}\left[\mathbbm{1}_{\mathcal{D}^{c}}\right] 
                    \mathbb{E}^{\mathbb{Q}}\left[Y\right] 
                    + 
                    \discountfactor
                    \text{Cov}^{\mathbb{Q}}\left(\mathbbm{1}_{\mathcal{D}^{c}}, Y\right) 
                    -
                    u
                    \mathbb{E}\left[\mathbbm{1}_{\mathcal{D}^{c}} \right]
                    \nonumber \\
                &= 
                    p^{\mathbb{Q}}
                    \left(
                        \pi + u
                    \right)
                    +
                    \discountfactor
                    \text{Cov}^{\mathbb{Q}}\left(\mathbbm{1}_{\mathcal{D}^{c}}, Y\right) 
                    -
                    p^{\mathbb{Q}}
                    u
                    \nonumber \\
                &=
                    p^{\mathbb{Q}}
                    \pi
                    -
                    \discountfactor
                    \text{Cov}^{\mathbb{Q}}\left(\mathbbm{1}_{\mathcal{D}}, Y\right) 
                \label{eqn:marginal-shareholder-value-cash-financing}
            \end{align}
        The derived equation only contains terms involving expectations of future cash flows,
        namely the payoff from the project.
        This reflects the fact that at time 0 there is no immediate value lost or gained
        for the shareholders, since, as the project is fairly priced, there is no difference
        in owning cash worth $u$ or a project worth $u$.

        Having derived the impact on equity valuation for these different funding types,
        a natural question to ask is which type of funding is preferred 
        from the shareholders perspective.
        This result can be obtained by comparing the three derived equations,
        which will be the result of the next section.

\end{document}